Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-03-24 demystify.tex
updates

\section{How much do \emph{I} cost?}\label{sec:ra-cost}
PhD students often ask why their salary is so low compared to ludicrous grants their advisers get. They also wonder why their offer letters sometimes show that their benefits higher than what they actually receive (i.e., stipend).

@@

At the end, the total budget comes out to be \$72K/year to support a PhD student. \emph{The summary is that over your 5--6 years of your PhD, you cost about \$400K, and while your stipend is X, your adviser probably pays 2X for you}.

>>>>

\section{How much do \emph{I} cost?}\label{sec:ra-cost}

PhD students often ask why their salary is so low compared to ludicrous grants their advisers get. They also wonder why their offer letters sometimes show that their benefits higher than what they actually receive (i.e., stipend).

@@

At the end, the total budget comes out to be \$72K/year to support a PhD student. \emph{The summary is that over your 5--6 years of your PhD, you cost about \$400K, and while your stipend is X, your adviser probably pays 2X for you}. But of course the nicest thing is that you do not have to pay for any of this! You get to gain the knowledge, do research, travel, (and don't even have to buy any research or computer equipments as mentioned in \autoref{sec:buying-equipment}) and also get paid!
